---
title: "R Scripts for Figures 2 and S3"
author: "Erick Motta"
---

### First Worker Recovery Experiment - Generalized linear mixed models

# Load packages:
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(MASS)
library(lme4)
library(interactions)
library(car)
library(effects)
library(emmeans)
library(tidyverse)
library(cowplot)
library(ggpubr)
library(patchwork) ### for plotting graphs together
library(gridExtra)
```

### ABSOLUTE ABUNDANCE DATA:
```{r Model}
wre_dada2_data <- read.table("tables/asv_tables/qiime2-WRE-feature-table-absolute.txt", header = T)
wre_dada2_data$Bee <- factor(wre_dada2_data$Bee)
wre_dada2_data$Description <- factor(wre_dada2_data$Description)
wre_dada2_data$Day <- factor(wre_dada2_data$Day)
```

# All bacteria:
```{r Model}
# linear_model <- glmer(Variable_effect ~ Fixed_effects + (1 | Nested_random_effects), family = poisson)

# glmer, allow to fit a generalized linear mixed-effects model: these models include a link function that allows to predict response variables with non-Gaussian distributions.

# if your outcome is discrete, i.e., you are dealing with counts (how many times something happen in given time interval), then the most common choice of the distribution to start with is Poisson distribution. The problem with Poisson distribution is that it is rather inflexible in the fact that it assumes that mean is equal to variance, if this assumption is not met, you may consider using quasi-Poisson family, or negative binomial distribution.

# Model:
wre_dada2_total_bact.m1 <- glmer(Total_bact ~ Description*Day + (1 | Bee), family = poisson, data = wre_dada2_data)
summary(wre_dada2_total_bact.m1)

# Description*Day effect:
wre_dada2_total_bact <- allEffects(wre_dada2_total_bact.m1)
print(wre_dada2_total_bact)

# Create a data frame:
df_wre_dada2_total_bact <- data.frame(wre_dada2_total_bact$`Description:Day`)

# Plot:
WRE_TB <- ggplot(data = df_wre_dada2_total_bact,
       aes(x = Day, y = fit, group = Description, color = Description)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), size = 1, width = 0, position = position_dodge(width = 0.4)) + 
  geom_line(size = 1, position = position_dodge(width = 0.4), alpha = 0.2, linetype = "dashed") +
  geom_point(size = 5, aes(shape=Description), position = position_dodge(width = 0.4)) +
  scale_shape_manual(values = c(16,17)) +
  scale_y_continuous(trans = "log10") + 
  scale_color_manual(values=c('#999999', '#E69F00')) +
  annotation_logticks(base = 10, side = "l") +
  ggtitle("All bacteria") +
  theme_classic() +
  theme(plot.title = element_text(face = "plain", size = 12, hjust = 0.5)) +
  theme(axis.text.x = element_text(color = "black", size = 10),
        axis.text.y = element_text(color = "black", size = 10)) +
  theme(axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 10)) +
  theme(legend.position = "none") +
  ylab(bquote('16S rRNA gene copies'))

# Statistical analysis:
emmeans(wre_dada2_total_bact.m1, pairwise~Description|Day)
```

# Snodgrassella:
```{r}
# Model:
wre_dada2_snod.m1 <- glmer(Snodgrassella ~ Description*Day + (1 | Bee), family = poisson, data = wre_dada2_data)
summary(wre_dada2_snod.m1)

# Description*Day effect:
wre_dada2_snod <- allEffects(wre_dada2_snod.m1)
print(wre_dada2_snod)

# Create a data frame:
df_wre_dada2_snod <- data.frame(wre_dada2_snod$`Description:Day`)

# Plot:
WRE_DADA2_SA <- ggplot(data = df_wre_dada2_snod,
       aes(x = Day, y = fit, group = Description, color = Description)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), size = 1, width = 0, position = position_dodge(width = 0.4)) + 
  geom_line(size = 1, position = position_dodge(width = 0.4), alpha = 0.2, linetype = "dashed") +
  geom_point(size = 5, aes(shape=Description), position = position_dodge(width = 0.4)) +
  scale_shape_manual(values = c(16,17)) +
  scale_y_continuous(trans = "log10") + 
  scale_color_manual(values=c('#999999', '#E69F00')) +
  annotation_logticks(base = 10, side = "l") +
  ggtitle("Snodgrassella") +
  theme_classic() +
  theme(plot.title = element_text(face = "italic", size = 12, hjust = 0.5)) +
  theme(axis.text.x = element_text(color = "black", size = 10),
        axis.text.y = element_text(color = "black", size = 10)) +
  theme(axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 10)) +
  theme(legend.position = "none") +
  ylab(bquote('16S rRNA gene copies'))

# Statistical analysis:
emmeans(wre_dada2_snod.m1, pairwise~Description|Day)
```

# Gilliamella:
```{r}
# Model:
wre_dada2_gill.m1 <- glmer(Gilliamella ~ Description*Day + (1 | Bee), family = poisson, data = wre_dada2_data)
summary(wre_dada2_gill.m1)

# Description*Day effect:
wre_dada2_gill <- allEffects(wre_dada2_gill.m1)
print(wre_dada2_gill)

# Create a data frame:
df_wre_dada2_gill <- data.frame(wre_dada2_gill$`Description:Day`)

# Plot:
WRE_DADA2_GI <- ggplot(data = df_wre_dada2_gill,
       aes(x = Day, y = fit, group = Description, color = Description)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), size = 1, width = 0, position = position_dodge(width = 0.4)) + 
  geom_line(size = 1, position = position_dodge(width = 0.4), alpha = 0.2, linetype = "dashed") +
  geom_point(size = 5, aes(shape=Description), position = position_dodge(width = 0.4)) +
  scale_shape_manual(values = c(16,17)) +
  scale_y_continuous(trans = "log10") + 
  scale_color_manual(values=c('#999999','#E69F00')) +
  annotation_logticks(base = 10, side = "l") +
  ggtitle("Gilliamella") +
  theme_classic() +
  theme(plot.title = element_text(face = "italic", size = 12, hjust = 0.5)) +
  theme(axis.text.x = element_text(color = "black", size = 10),
        axis.text.y = element_text(color = "black", size = 10)) +
  theme(axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 10)) +
  theme(legend.position = "none") +
  ylab(bquote('16S rRNA gene copies'))

# Statistical analysis:
emmeans(wre_dada2_gill.m1, pairwise~Description|Day)
```

# Bifidobacterium:
```{r}
# Model:
wre_dada2_bifido.m1 <- glmer(Bifidobacterium ~ Description*Day + (1 | Bee), family = poisson, data = wre_dada2_data)
summary(wre_dada2_bifido.m1)

# Description*Day effect:
wre_dada2_bifido <- allEffects(wre_dada2_bifido.m1)
print(wre_dada2_bifido)

# Create a data frame:
df_wre_dada2_bifido <- data.frame(wre_dada2_bifido$`Description:Day`)

# Plot:
WRE_DADA2_BI <- ggplot(data = df_wre_dada2_bifido,
       aes(x = Day, y = fit, group = Description, color = Description)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), size = 1, width = 0, position = position_dodge(width = 0.4)) + 
  geom_line(size = 1, position = position_dodge(width = 0.4), alpha = 0.2, linetype = "dashed") +
  geom_point(size = 5, aes(shape=Description), position = position_dodge(width = 0.4)) +
  scale_shape_manual(values = c(16,17)) +
  scale_y_continuous(trans = "log10") + 
  scale_color_manual(values=c('#999999','#E69F00')) +
  annotation_logticks(base = 10, side = "l") +
  ggtitle("Bifidobacterium") +
  theme_classic() +
  theme(plot.title = element_text(face = "italic", size = 12, hjust = 0.5)) +
  theme(axis.text.x = element_text(color = "black", size = 10),
        axis.text.y = element_text(color = "black", size = 10)) +
  theme(axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 10)) +
  theme(legend.position = "none") +
  ylab(bquote('16S rRNA gene copies'))

# Statistical analysis:
emmeans(wre_dada2_bifido.m1, pairwise~Description|Day)
```

# Lactobacillus Firm-5:
```{r}
# Model:
wre_dada2_firm5.m1 <- glmer(Firm5 ~ Description*Day + (1 | Bee), family = poisson, data = wre_dada2_data)
summary(wre_dada2_firm5.m1)

# Description*Day effect:
wre_dada2_firm5 <- allEffects(wre_dada2_firm5.m1)
print(wre_dada2_firm5)

# Create a data frame:
df_wre_dada2_firm5 <- data.frame(wre_dada2_firm5$`Description:Day`)

# Plot:
WRE_DADA2_F5 <- ggplot(data = df_wre_dada2_firm5,
       aes(x = Day, y = fit, group = Description, color = Description)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), size = 1, width = 0, position = position_dodge(width = 0.4)) + 
  geom_line(size = 1, position = position_dodge(width = 0.4), alpha = 0.2, linetype = "dashed") +
  geom_point(size = 5, aes(shape=Description), position = position_dodge(width = 0.4)) +
  scale_shape_manual(values = c(16,17)) +
  scale_y_continuous(trans = "log10") + 
  scale_color_manual(values=c('#999999','#E69F00')) +
  annotation_logticks(base = 10, side = "l") +
  ggtitle("Lactobacillus Firm-5") +
  theme_classic() +
  theme(plot.title = element_text(face = "italic", size = 12, hjust = 0.5)) +
  theme(axis.text.x = element_text(color = "black", size = 10),
        axis.text.y = element_text(color = "black", size = 10)) +
  theme(axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 10)) +
  theme(legend.position = "none") +
  ylab(bquote('16S rRNA gene copies'))

# Statistical analysis:
emmeans(wre_dada2_firm5.m1, pairwise~Description|Day)
```

# Lactobacillus Firm-4:
```{r}
wre_dada2_firm4.m1 <- glmer(Firm4 ~ Description*Day + (1 | Bee), family = poisson, data = wre_dada2_data)
summary(wre_dada2_firm4.m1)

# Statistical analysis:
emmeans(wre_dada2_firm4.m1, pairwise~Description|Day)
```

# Frischella:
```{r}
wre_dada2_fris.m1 <- glmer(Frischella ~ Description*Day + (1 | Bee), family = poisson, data = wre_dada2_data)
summary(wre_dada2_fris.m1)

# Statistical analysis:
emmeans(wre_dada2_fris.m1, pairwise~Description|Day)
```

# Bartonella:
```{r Model}
wre_dada2_bart.m1 <- glmer(Bartonella ~ Description*Day + (1 | Bee), family = poisson, data = wre_dada2_data)
summary(wre_dada2_bart.m1)

# Statistical analysis:
emmeans(wre_dada2_bart.m1, pairwise~Description|Day)
```

# Other bacteria:
```{r Model}
wre_dada2_other_bact.m1 <- glmer(Other_bact ~ Description*Day + (1 | Bee), family = poisson, data = wre_dada2_data)
summary(wre_dada2_other_bact.m1)

# Statistical analysis:
emmeans(wre_dada2_other_bact.m1, pairwise~Description|Day)
```


### RELATIVE ABUNDANCE DATA:
```{r Model}
wre_dada2_rel <- read.table("tables/asv_tables/qiime2-WRE-feature-table-relative.txt", header = T)
wre_dada2_rel$Bee <- factor(wre_dada2_rel$Bee)
wre_dada2_rel$Description <- factor(wre_dada2_rel$Description)
wre_dada2_rel$Day <- factor(wre_dada2_rel$Day)
```

# Snodgrasssella relative abundance:
```{r}
# Model:
wre_dada2_snod_rel.m1 <- glmer(Snodgrassella ~ Description*Day + (1 | Bee), family = poisson, data = wre_dada2_rel)
summary(wre_dada2_snod_rel.m1)

# Statistical analysis:
emmeans(wre_dada2_snod_rel.m1, pairwise~Description|Day)

# Plot:
emmip(wre_dada2_snod_rel.m1, Description~Day, CIs = TRUE)
```

# Bifidobacterium relative abundance:
```{r}
# Model:
wre_dada2_bifido_rel.m1 <- glmer(Bifidobacterium ~ Description*Day + (1 | Bee), family = poisson, data = wre_dada2_rel)
summary(wre_dada2_bifido_rel.m1)

# Statistical analysis:
emmeans(wre_dada2_bifido_rel.m1, pairwise~Description|Day)

# Plot:
emmip(wre_dada2_bifido_rel.m1, Description~Day, CIs = TRUE)
```

# Lactobacillus Firm-5 relative abundance:
```{r}
# Model:
wre_dada2_firm5_rel.m1 <- glmer(Firm5 ~ Description*Day + (1 | Bee), family = poisson, data = wre_dada2_rel)
summary(wre_dada2_firm5_rel.m1)

# Statistical analysis:
emmeans(wre_dada2_firm5_rel.m1, pairwise~Description|Day)

# Plot:
emmip(wre_dada2_firm5_rel.m1, Description~Day, CIs = TRUE)
```

# Lactobacillus Firm-4 relative abundance:
```{r}
# Model:
wre_dada2_firm4_rel.m1 <- glmer(Firm4 ~ Description*Day + (1 | Bee), family = poisson, data = wre_dada2_rel)
summary(wre_dada2_firm4_rel.m1)

# Statistical analysis:
emmeans(wre_dada2_firm4_rel.m1, pairwise~Description|Day)

# Plot:
emmip(wre_dada2_firm4_rel.m1, Description~Day, CIs = TRUE)
```

# Gilliamella relative abundance:
```{r}
# Model:
wre_dada2_gill_rel.m1 <- glmer(Gilliamella ~ Description*Day + (1 | Bee), family = poisson, data = wre_dada2_rel)
summary(wre_dada2_gill_rel.m1)

# Statistical analysis:
emmeans(wre_dada2_gill_rel.m1, pairwise~Description|Day)

# Plot:
emmip(wre_dada2_gill_rel.m1, Description~Day, CIs = TRUE)
```


### Second worker recovery experiment - June, 2019 qPCR data, Total bacteria and Snodgrassella abundances at days 0 and 3 post-treatment

# Snodgrassella:
```{r}
# Model:
wre2_qpcr_data <- read.table("tables/qPCR-WRE-experiment2.txt", header = T)
wre2_qpcr_data$Bee <- factor(wre2_qpcr_data$Bee)
wre2_qpcr_data$Description <- factor(wre2_qpcr_data$Description)
wre2_qpcr_data$Day <- factor(wre2_qpcr_data$Day)

wre2_qpcr_snod.m1 <- glmer(Snodgrassella ~ Description*Day + (1 | Bee), family = poisson, data = wre2_qpcr_data)
summary(wre2_qpcr_snod.m1)

# Description*Day effect:
wre2_qpcr_snod <- allEffects(wre2_qpcr_snod.m1)
print(wre2_qpcr_snod)

# Create a data frame:
df_wre2_qpcr_snod <- data.frame(wre2_qpcr_snod$`Description:Day`)

# Plot:
WRE2_QPCR_SA <- ggplot(data = df_wre2_qpcr_snod,
       aes(x = Day, y = fit, group = Description, color = Description)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), size = 1, width = 0, position = position_dodge(width = 0.4)) + 
  geom_line(size = 1, position = position_dodge(width = 0.4), alpha = 0.2, linetype = "dashed") +
  geom_point(aes(shape=Description), size = 5, position = position_dodge(width = 0.4)) +
  scale_shape_manual(values = c(16,17)) +
  scale_y_continuous(trans = "log10") + 
  scale_color_manual(values=c('#999999', '#E69F00')) +
  annotation_logticks(base = 10, side = "l") +
  ggtitle("Snodgrassella") +
  theme_classic() +
  theme(plot.title = element_text(face = "italic", size = 12, hjust = 0.5)) +
  theme(axis.text.x = element_text(color = "black", size = 10),
        axis.text.y = element_text(color = "black", size = 10)) +
  theme(axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 8)) +
  theme(legend.position = "none") +
  ylab(bquote('16S rRNA gene copies'))

# Statistical analysis:
emmeans(wre2_qpcr_snod.m1, pairwise~Description|Day)
```

# All bacteria:
```{r}
# Model:
wre2_qpcr_total.m1 <- glmer(Total_bact ~ Description*Day + (1 | Bee), family = poisson, data = wre2_qpcr_data)
summary(wre2_qpcr_total.m1)

# Description*Day effect:
wre2_qpcr_total <- allEffects(wre2_qpcr_total.m1)
print(wre2_qpcr_total)

# Create a data frame:
df_wre2_qpcr_total <- data.frame(wre2_qpcr_total$`Description:Day`)

# Plot:
WRE2_QPCR_TB <- ggplot(data = df_wre2_qpcr_total,
       aes(x = Day, y = fit, group = Description, color = Description)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), size = 1, width = 0, position = position_dodge(width = 0.4)) + 
  geom_line(size = 1, position = position_dodge(width = 0.4), alpha = 0.2, linetype = "dashed") +
  geom_point(aes(shape=Description), size = 5, position = position_dodge(width = 0.4)) +
  scale_shape_manual(values = c(16,17)) +
  scale_y_continuous(trans = "log10") + 
  scale_color_manual(values=c('#999999', '#E69F00')) +
  annotation_logticks(base = 10, side = "l") +
  ggtitle("All bacteria") +
  theme_classic() +
  theme(plot.title = element_text(face = "plain", size = 12, hjust = 0.5)) +
  theme(axis.text.x = element_text(color = "black", size = 10),
        axis.text.y = element_text(color = "black", size = 10)) +
  theme(axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 8)) +
  theme(legend.position = "none") +
  ylab(bquote('16S rRNA gene copies'))

# Statistical analysis:
emmeans(wre2_qpcr_total.m1, pairwise~Description|Day)
```

### Third worker recovery experiment - June, 2019 qPCR data for Snodgrassella abundance at days 0 and 3 post-treatment

# Snodgrassella:
```{r}
# Model:
wre3_qpcr_data <- read.table("tables/qPCR-WRE-experiment3.txt", header = T)
wre3_qpcr_data$Bee <- factor(wre3_qpcr_data$Bee)
wre3_qpcr_data$Description <- factor(wre3_qpcr_data$Description)
wre3_qpcr_data$Day <- factor(wre3_qpcr_data$Day)

wre3_qpcr_snod.m1 <- glmer(Snodgrassella ~ Description*Day + (1 | Bee), family = poisson, data = wre3_qpcr_data)
summary(wre3_qpcr_snod.m1)

# Description*Day effect:
wre3_qpcr_snod <- allEffects(wre3_qpcr_snod.m1)
print(wre3_qpcr_snod)

# Create a data frame:
df_wre3_qpcr_snod <- data.frame(wre3_qpcr_snod$`Description:Day`)

# Plot:
WRE3_QPCR_SA <- ggplot(data = df_wre3_qpcr_snod,
       aes(x = Day, y = fit, group = Description, color = Description)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), size = 1, width = 0, position = position_dodge(width = 0.4)) + 
  geom_line(size = 1, position = position_dodge(width = 0.4), alpha = 0.2, linetype = "dashed") +
  geom_point(aes(shape=Description), size = 5, position = position_dodge(width = 0.4)) +
  scale_shape_manual(values = c(16,17)) +
  scale_y_continuous(trans = "log10") + 
  scale_color_manual(values=c('#999999', '#E69F00')) +
  annotation_logticks(base = 10, side = "l") +
  ggtitle("Snodgrassella") +
  theme_classic() +
  theme(plot.title = element_text(face = "italic", size = 12, hjust = 0.5)) +
  theme(axis.text.x = element_text(color = "black", size = 10),
        axis.text.y = element_text(color = "black", size = 10)) +
  theme(axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 8)) +
  theme(legend.position = "none") +
  ylab(bquote('16S rRNA gene copies'))

# Statistical analysis:
emmeans(wre3_qpcr_snod.m1, pairwise~Description|Day)
```


### RECOVERY RATES DATA:
# Oral exposure - Hive recovery experiments:
```{r Model}
### Hive 8, October 2018
df <- data.frame(supp=rep(c("Recovered", "Non-recovered"), each=2),
                 group=rep(c("Control", "0.1% Roundup"), 2),
                 len=c(153, 96, 195, 252))
head(df)

df$group <- factor(df$group, levels = c("Control", "0.1% Roundup"))

rec_fall_2018 <- ggplot(data = df, aes(x = group, y = len, fill = supp)) +
  geom_bar(stat = "identity") +
  scale_fill_manual("len", values = c("Non-recovered" = "#CCCCCB", "Recovered" = "black")) +
  scale_y_continuous("Bees recovered on Day 3", breaks = c(0, 50, 100, 150, 200, 250, 300, 350)) +
  ggtitle("Experiment 1, October 2018") +
  theme(plot.title = element_text(size = 12, face = "plain")) +
  theme(legend.position = "bottom") +
  theme(legend.title = element_blank()) +
  theme(axis.title.x = element_blank()) +
  theme(axis.text.x = element_text(color = "black", size = 10),
        axis.text.y = element_text(color = "black", size = 10)) +
  theme(axis.title.y = element_text(size = 10))

### Hive 9, June 2019
df.2 <- data.frame(supp=rep(c("Recovered", "Non-recovered"), each=2),
                 group=rep(c("Control", "0.1% Roundup"), 2),
                 len=c(192, 159, 138, 171))
head(df.2)

df.2$group <- factor(df.2$group, levels = c("Control", "0.1% Roundup"))

rec_jun_2019 <- ggplot(data = df.2, aes(x = group, y = len, fill = supp)) +
  geom_bar(stat = "identity") +
  scale_fill_manual("len", values = c("Non-recovered" = "#CCCCCB", "Recovered" = "black")) +
  scale_y_continuous("Bees recovered on Day 3", breaks = c(0, 50, 100, 150, 200, 250, 300, 350)) +
  ggtitle("Experiment 2, June 2019") +
  theme(plot.title = element_text(size = 12, face = "plain")) +
  theme(legend.position = "bottom") +
  theme(legend.title = element_blank()) +
  theme(axis.title.x = element_blank()) +
  theme(axis.text.x = element_text(color = "black", size = 10),
        axis.text.y = element_text(color = "black", size = 10)) +
  theme(axis.title.y = element_text(size = 10))

### Hive 8, June 2019
df.3 <- data.frame(supp=rep(c("Recovered", "Non-recovered"), each=2),
                 group=rep(c("Control", "0.1% Roundup"), 2),
                 len=c(268, 258, 122, 132))
head(df.3)

df.3$group <- factor(df.3$group, levels = c("Control", "0.1% Roundup"))

rec_jun2_2019 <- ggplot(data = df.3, aes(x = group, y = len, fill = supp)) +
  geom_bar(stat = "identity") +
  scale_fill_manual("len", values = c("Non-recovered" = "#CCCCCB", "Recovered" = "black")) +
  scale_y_continuous("Bees recovered on Day 3", breaks = c(0, 60, 120, 180, 240, 300, 360, 420)) +
  ggtitle("Experiment 3, June 2019") +
  theme(plot.title = element_text(size = 12, face = "plain")) +
  theme(legend.position = "bottom") +
  theme(legend.title = element_blank()) +
  theme(axis.title.x = element_blank()) +
  theme(axis.text.x = element_text(color = "black", size = 10),
        axis.text.y = element_text(color = "black", size = 10)) +
  theme(axis.title.y = element_text(size = 10))

### Hive 8, July 2019
df.4 <- data.frame(supp=rep(c("Recovered", "Non-recovered"), each=2),
                 group=rep(c("Control", "0.1% Roundup"), 2),
                 len=c(94, 97, 259, 256))
head(df.4)

df.4$group <- factor(df.4$group, levels = c("Control", "0.1% Roundup"))

rec_jul_2019 <- ggplot(data = df.4, aes(x = group, y = len, fill = supp)) +
  geom_bar(stat = "identity") +
  scale_fill_manual("len", values = c("Non-recovered" = "#CCCCCB", "Recovered" = "black")) +
  scale_y_continuous("Bees recovered on Day 3", breaks = c(0, 50, 100, 150, 200, 250, 300, 350)) +
  ggtitle("Experiment 4, July 2019") +
  theme(plot.title = element_text(size = 12, face = "plain")) +
  theme(legend.position = "bottom") +
  theme(legend.title = element_blank()) +
  theme(axis.title.x = element_blank()) +
  theme(axis.text.x = element_text(color = "black", size = 10),
        axis.text.y = element_text(color = "black", size = 10)) +
  theme(axis.title.y = element_text(size = 10))

### Hive 8, July 2019
df.5 <- data.frame(supp=rep(c("Recovered", "Non-recovered"), each=2),
                 group=rep(c("Control", "0.1% Roundup"), 2),
                 len=c(64, 37, 376, 403))
head(df.5)

df.5$group <- factor(df.5$group, levels = c("Control", "0.1% Roundup"))

rec_jul2_2019 <- ggplot(data = df.5, aes(x = group, y = len, fill = supp)) +
  geom_bar(stat = "identity") +
  scale_fill_manual("len", values = c("Non-recovered" = "#CCCCCB", "Recovered" = "black")) +
  scale_y_continuous("Bees recovered on Day 3", breaks = c(0, 60, 120, 180, 240, 300, 360, 420)) +
  ggtitle("Experiment 5, July 2019") +
  theme(plot.title = element_text(size = 12, face = "plain")) +
  theme(legend.position = "bottom") +
  theme(legend.title = element_blank()) +
  theme(axis.title.x = element_blank()) +
  theme(axis.text.x = element_text(color = "black", size = 10),
        axis.text.y = element_text(color = "black", size = 10)) +
  theme(axis.title.y = element_text(size = 10))

### Validation, hive 9, july 2019
df.6 <- data.frame(supp=rep(c("Recovered", "Non-recovered"), each=2),
                 group=rep(c("White", "Pink"), 2),
                 len=c(120, 117, 58, 59))
head(df.6)

df.6$group <- factor(df.6$group, levels = c("White", "Pink"))

val_jul_2019 <- ggplot(data = df.6, aes(x = group, y = len, fill = supp)) +
  geom_bar(stat = "identity") +
  scale_fill_manual("len", values = c("Non-recovered" = "#CCCCCB", "Recovered" = "black")) +
  scale_y_continuous("Bees recovered on Day 3", breaks = c(0, 30, 60, 90, 120, 150, 180)) +
  ggtitle("Validation experiment") +
  theme(plot.title = element_text(size = 12, face = "plain")) +
  theme(legend.position = "bottom") +
  theme(legend.title = element_blank()) +
  theme(axis.title.x = element_blank()) +
  theme(axis.text.x = element_text(color = "black", size = 10),
        axis.text.y = element_text(color = "black", size = 10)) +
  theme(axis.title.y = element_text(size = 10))
```


# Plotting Figure 2 and Figure S3:
```{r}
### Figure 2:
plot_grid(rec_fall_2018, WRE_TB, WRE_DADA2_SA, WRE_DADA2_GI, WRE_DADA2_BI, WRE_DADA2_F5, labels = "AUTO", nrow = 2)

### Figure S3:
plot_grid(rec_jun_2019, WRE2_QPCR_TB, WRE2_QPCR_SA, rec_jun2_2019, WRE3_QPCR_SA, rec_jul_2019, rec_jul2_2019, val_jul_2019, labels = "AUTO", nrow = 3)
```
