---
title: "R Scripts for Figures 3-BCD and S4"
author: "Erick Motta"
---

### Field experiment performed in site 1, Driftwood, TX, 2018 - Generalized linear mixed models

# Load packages:
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(MASS)
library(lme4)
library(interactions)
library(car)
library(effects)
library(emmeans)
library(tidyverse)
library(ggplot2)
library(cowplot)
library(gridExtra)
```

# For all bacteria:
```{r}
out_hive_dada2 <- read.table("tables/asv_tables/qiime2-DW-site1-2018-feature-table-absolute.txt", header = T)
out_hive_dada2$Bee <- factor(out_hive_dada2$Bee)
out_hive_dada2$Group <- factor(out_hive_dada2$Group)
out_hive_dada2$Description <- factor(out_hive_dada2$Description)
out_hive_dada2$Hive <- factor(out_hive_dada2$Hive)
out_hive_dada2$Week <- factor(out_hive_dada2$Week)

# linear_model <- glmer(Variable_effect ~ Fixed_effects + (1 | Nested_random_effects), family = poisson)

# glmer, allow to fit a generalized linear mixed-effects model: these models include a link function that allows to predict response variables with non-Gaussian distributions.

# if your outcome is discrete, i.e., you are dealing with counts (how many times something happen in given time interval), then the most common choice of the distribution to start with is Poisson distribution. The problem with Poisson distribution is that it is rather inflexible in the fact that it assumes that mean is equal to variance, if this assumption is not met, you may consider using quasi-Poisson family, or negative binomial distribution.

# Model
oh_tb_dada2.m1 <- glmer(Total_bact ~ Description*Week + (1 | Hive/Bee), family = poisson, data = out_hive_dada2)
summary(oh_tb_dada2.m1)

# anova
Anova(oh_tb_dada2.m1)

# Description*Week effect
oh_tb_dada2 <- allEffects(oh_tb_dada2.m1)
print(oh_tb_dada2)

# Create a data frame
df_oh_tb_dada2 <- data.frame(oh_tb_dada2$`Description:Week`)

# Statistical analysis
emmeans(oh_tb_dada2.m1, pairwise~Description|Week)

# Plot
OH_TB_dada2 <- ggplot(data = df_oh_tb_dada2,
       aes(x = Week, y = fit, group = Description, color = Description)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), size = 1, width = 0, position = position_dodge(width = 0.4)) + 
  geom_line(size = 1, position = position_dodge(width = 0.4), alpha = 0.2, linetype = "dashed") +
  geom_point(size = 4, aes(shape = Description), position = position_dodge(width = 0.4)) +
  scale_shape_manual(values = c(16,17)) +
  scale_y_continuous(breaks = c(1e+7,2e+7,3e+7,4e+7,5e+7), trans = "log10") + 
  scale_color_manual(values=c('#999999', '#E69F00')) +
  annotation_logticks(base = 10, side = "l") +
  theme_classic() +
  ggtitle("All bacteria") +
  theme(plot.title = element_text(face = "plain", size = 10, hjust = 0.5)) +
  theme(axis.text.x = element_text(color = "black", size = 10),
        axis.text.y = element_text(color = "black", size = 10)) +
  theme(axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 10)) +
  ylab(bquote(~Log[10]~ '16S rDNA copies')) +
  theme(legend.position = "none")
```

# For Snodgrassella:
```{r}
# Model
oh_snod_dada2.m1 <- glmer(Snodgrassella ~ Description*Week + (1 | Hive/Bee), family = poisson, data = out_hive_dada2)
summary(oh_snod_dada2.m1)

# anova
Anova(oh_snod_dada2.m1)

# Description*Week effect
oh_snod_dada2 <- allEffects(oh_snod_dada2.m1)
print(oh_snod_dada2)

# Create a data frame
df_oh_snod_dada2 <- data.frame(oh_snod_dada2$`Description:Week`)

# Statistical analysis
emmeans(oh_snod_dada2.m1, pairwise~Description|Week)

# Plot
OH_SA_dada2 <- ggplot(data = df_oh_snod_dada2,
       aes(x = Week, y = fit, group = Description, color = Description)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), size = 1, width = 0, position = position_dodge(width = 0.4)) + 
  geom_line(size = 1, position = position_dodge(width = 0.4), alpha = 0.2, linetype = "dashed") +
  geom_point(size = 4, aes(shape = Description), position = position_dodge(width = 0.4)) +
  scale_shape_manual(values = c(16,17)) +  scale_y_continuous(trans = "log10") + 
  scale_color_manual(values=c('#999999', '#E69F00')) +
  annotation_logticks(base = 10, side = "l") +
  theme_classic() +
  ggtitle("Snodgrassella alvi") +
  theme(plot.title = element_text(face = "italic", size = 10, hjust = 0.5)) +
  theme(axis.text.x = element_text(color = "black", size = 10),
        axis.text.y = element_text(color = "black", size = 10)) +
  theme(axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 10)) +
  ylab(bquote(~Log[10]~ '16S rDNA copies')) +
  theme(legend.position = "none")
```

# For Bifidobacterium:
```{r}
# Model
oh_bifido_dada2.m1 <- glmer(Bifidobacterium ~ Description*Week + (1 | Hive/Bee), family = poisson, data = out_hive_dada2)
summary(oh_bifido_dada2.m1)

# anova
Anova(oh_bifido_dada2.m1)

# Description*Week effect
oh_bifido_dada2 <- allEffects(oh_bifido_dada2.m1)
print(oh_bifido_dada2)

# Create a data frame
df_oh_bifido_dada2 <- data.frame(oh_bifido_dada2$`Description:Week`)

# Statistical analysis
emmeans(oh_bifido_dada2.m1, pairwise~Description|Week)

# Plot
OH_BI_dada2 <- ggplot(data = df_oh_bifido_dada2,
       aes(x = Week, y = fit, group = Description, color = Description)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), size = 1, width = 0, position = position_dodge(width = 0.4)) + 
  geom_line(size = 1, position = position_dodge(width = 0.4), alpha = 0.2, linetype = "dashed") +
  geom_point(size = 4, aes(shape = Description), position = position_dodge(width = 0.4)) +
  scale_shape_manual(values = c(16,17)) +
  scale_y_continuous(trans = "log10") + 
  scale_color_manual(values=c('#999999', '#E69F00')) +
  annotation_logticks(base = 10, side = "l") +
  theme_classic() +
  ggtitle("Bifidobacterium spp.") +
  theme(plot.title = element_text(face = "italic", size = 10, hjust = 0.5)) +
  theme(axis.text.x = element_text(color = "black", size = 10),
        axis.text.y = element_text(color = "black", size = 10)) +
  theme(axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 10)) +
  ylab(bquote(~Log[10]~ '16S rDNA copies')) +
  theme(legend.position = "none")
```

# For Lactobacillus Firm-4:
```{r}
# Model
oh_firm4_dada2.m1 <- glmer(Firm4 ~ Description*Week + (1 | Hive/Bee), family = poisson, data = out_hive_dada2)
summary(oh_firm4_dada2.m1)

# anova
Anova(oh_firm4_dada2.m1)

# Description*Time effect
oh_firm4_dada2 <- allEffects(oh_firm4_dada2.m1)
print(oh_firm4_dada2)

# Create a data frame
df_oh_firm4_dada2 <- data.frame(oh_firm4_dada2$`Description:Week`)

# Statistical analysis
emmeans(oh_firm4_dada2.m1, pairwise~Description|Week)

# Plot
OH_F4_dada2 <- ggplot(data = df_oh_firm4_dada2,
       aes(x = Week, y = fit, group = Description, color = Description)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), size = 1, width = 0, position = position_dodge(width = 0.4)) + 
  geom_line(size = 1, position = position_dodge(width = 0.4), alpha = 0.2, linetype = "dashed") +
  geom_point(size = 4, aes(shape = Description), position = position_dodge(width = 0.4)) +
  scale_shape_manual(values = c(16,17)) +
  scale_y_continuous(trans = "log10") + 
  scale_color_manual(values=c('#999999', '#E69F00')) +
  annotation_logticks(base = 10, side = "l") +
  theme_classic() +
  ggtitle("Lactobacillus Firm-4") +
  theme(plot.title = element_text(face = "italic", size = 10, hjust = 0.5)) +
  theme(axis.text.x = element_text(color = "black", size = 10),
        axis.text.y = element_text(color = "black", size = 10)) +
  theme(axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 10)) +
  ylab(bquote(~Log[10]~ '16S rDNA copies')) +
  theme(legend.position = "none")
```

# For Lactobacillus Firm-4 - L. mellis
```{r}
# Model
oh_mellis_dada2.m2 <- glmer(L_mellis ~ Description*Week + (1 | Hive/Bee), family = poisson, data = out_hive_dada2)
# Model failed and tried to increase the number of iterations, based on this reference: https://rstudio-pubs-static.s3.amazonaws.com/33653_57fc7b8e5d484c909b615d8633c01d51.html)
la <- getME(oh_mellis_dada2.m2, c("theta", "fixef"))
oh_mellis_dada2.m1 <- update(oh_mellis_dada2.m2, start = la, control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5)))
summary(oh_mellis_dada2.m1)

# anova
Anova(oh_mellis_dada2.m1)

# Description*Week effect
oh_mellis_dada2 <- allEffects(oh_mellis_dada2.m1)
print(oh_mellis_dada2)

# Create a data frame
df_oh_mellis_dada2 <- data.frame(oh_mellis_dada2$`Description:Week`)

# Statistical analysis
emmeans(oh_mellis_dada2.m1, pairwise~Description|Week)

# Plot
OH_mellis_dada2 <- ggplot(data = df_oh_mellis_dada2,
       aes(x = Week, y = fit, group = Description, color = Description)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), size = 1, width = 0, position = position_dodge(width = 0.4)) + 
  geom_line(size = 1, position = position_dodge(width = 0.4), alpha = 0.2, linetype = "dashed") +
  geom_point(size = 4, aes(shape = Description), position = position_dodge(width = 0.4)) +
  scale_shape_manual(values = c(16,17)) +
  scale_y_continuous(trans = "log10") + 
  scale_color_manual(values=c('#999999', '#E69F00')) +
  annotation_logticks(base = 10, side = "l") +
  theme_classic() +
  ggtitle("Lactobacillus mellis") +
  theme(plot.title = element_text(face = "italic", size = 10, hjust = 0.5)) +
  theme(axis.text.x = element_text(color = "black", size = 10),
        axis.text.y = element_text(color = "black", size = 10)) +
  theme(axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 10)) +
  ylab(bquote(~Log[10]~ '16S rDNA copies')) +
  theme(legend.position = "none")
```

# For Lactobacillus Firm-4 - L. mellifer
```{r}
# Model
oh_mellifer_dada2.m2 <- glmer(L_mellifer ~ Description*Week + (1 | Hive/Bee), family = poisson, data = out_hive_dada2)
# Model failed and tried to increase the number of iterations, based on this reference: https://rstudio-pubs-static.s3.amazonaws.com/33653_57fc7b8e5d484c909b615d8633c01d51.html)
lm <- getME(oh_mellifer_dada2.m2, c("theta", "fixef"))
oh_mellifer_dada2.m1 <- update(oh_mellifer_dada2.m2, start = lm, control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5)))
summary(oh_firm4_dada2.m1)

# anova
Anova(oh_mellifer_dada2.m1)

# Description*Time effect
oh_mellifer_dada2 <- allEffects(oh_mellifer_dada2.m1)
print(oh_mellifer_dada2)

# Create a data frame
df_oh_mellifer_dada2 <- data.frame(oh_mellifer_dada2$`Description:Week`)

# Statistical analysis
emmeans(oh_mellifer_dada2.m1, pairwise~Description|Week)

# Plot
OH_mellifer_dada2 <- ggplot(data = df_oh_mellifer_dada2,
       aes(x = Week, y = fit, group = Description, color = Description)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), size = 1, width = 0, position = position_dodge(width = 0.4)) + 
  geom_line(size = 1, position = position_dodge(width = 0.4), alpha = 0.2, linetype = "dashed") +
  geom_point(size = 4, aes(shape = Description), position = position_dodge(width = 0.4)) +
  scale_shape_manual(values = c(16,17)) +
  scale_y_continuous(trans = "log10") + 
  scale_color_manual(values=c('#999999', '#E69F00')) +
  annotation_logticks(base = 10, side = "l") +
  theme_classic() +
  ggtitle("Lactobacillus mellifer") +
  theme(plot.title = element_text(face = "italic", size = 10, hjust = 0.5)) +
  theme(axis.text.x = element_text(color = "black", size = 10),
        axis.text.y = element_text(color = "black", size = 10)) +
  theme(axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 10)) +
  ylab(bquote(~Log[10]~ '16S rDNA copies')) +
  theme(legend.position = "none")
```

# For Lactobacillus Firm-5:
```{r}
# Model
oh_firm5_dada2.m1 <- glmer(Firm5 ~ Description*Week + (1 | Hive/Bee), family = poisson, data = out_hive_dada2)
summary(oh_firm5_dada2.m1)

# anova
Anova(oh_firm5_dada2.m1)

# Description*Week effect
oh_firm5_dada2 <- allEffects(oh_firm5_dada2.m1)
print(oh_firm5_dada2)

# Create a data frame
df_oh_firm5_dada2 <- data.frame(oh_firm5_dada2$`Description:Week`)

# Statistical analysis
emmeans(oh_firm5_dada2.m1, pairwise~Description|Week)

# Plot
OH_F5_dada2 <- ggplot(data = df_oh_firm5_dada2,
       aes(x = Week, y = fit, group = Description, color = Description)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), size = 1, width = 0, position = position_dodge(width = 0.4)) + 
  geom_line(size = 1, position = position_dodge(width = 0.4), alpha = 0.2, linetype = "dashed") +
  geom_point(size = 4, aes(shape = Description), position = position_dodge(width = 0.4)) +
  scale_shape_manual(values = c(16,17)) +
  scale_y_continuous(trans = "log10") +
  scale_color_manual(values=c('#999999', '#E69F00')) +
  annotation_logticks(base = 10, side = "l") +
  theme_classic() +
  ggtitle("Lactobacillus Firm-5") +
  theme(plot.title = element_text(face = "italic", size = 10, hjust = 0.5)) +
  theme(axis.text.x = element_text(color = "black", size = 10), 
        axis.text.y = element_text(color = "black", size = 10)) +
  theme(axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 10)) +
  ylab(bquote(~Log[10]~ '16S rDNA copies')) +
  theme(legend.position = "none")
```

# For Lactobacillus Firm-5 - Lactobacillus apis
```{r Model}
oh_lapis_dada2.m1 <- glmer(L_apis ~ Description*Week + (1 | Hive/Bee), family = poisson, data = out_hive_dada2)
summary(oh_lapis_dada2.m1)

# anova
Anova(oh_lapis_dada2.m1)

# Description*Week effect
oh_lapis_dada2 <- allEffects(oh_lapis_dada2.m1)
print(oh_lapis_dada2)

# Create a data frame
df_oh_lapis_dada2 <- data.frame(oh_lapis_dada2$`Description:Week`)

# Statistical analysis
emmeans(oh_lapis_dada2.m1, pairwise~Description|Week)

# Plot
OH_Lapis_dada2 <- ggplot(data = df_oh_lapis_dada2,
       aes(x = Week, y = fit, group = Description, color = Description)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), size = 1, width = 0, position = position_dodge(width = 0.4)) + 
  geom_line(size = 1, position = position_dodge(width = 0.4), alpha = 0.2, linetype = "dashed") +
  geom_point(size = 4, aes(shape = Description), position = position_dodge(width = 0.4)) +
  scale_shape_manual(values = c(16,17)) +
  scale_y_continuous(trans = "log10") + 
  scale_color_manual(values=c('#999999', '#E69F00')) +
  annotation_logticks(base = 10, side = "l") +
  theme_classic() +
  ggtitle("Lactobacillus apis") +
  theme(plot.title = element_text(face = "italic", size = 10, hjust = 0.5)) +
  theme(axis.text.x = element_text(color = "black", size = 10), 
        axis.text.y = element_text(color = "black", size = 10)) +
  theme(axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 10)) +
  ylab(bquote(~Log[10]~ '16S rDNA copies')) +
  theme(legend.position = "none")
```

# For Lactobacillus Firm-5 - Lactobacillus helsingborgensis
```{r}
# Model
oh_Lhels_dada2.m1 <- glmer(L_helsingborgensis ~ Description*Week + (1 | Hive/Bee), family = poisson, data = out_hive_dada2)
summary(oh_Lhels_dada2.m1)

# anova
Anova(oh_Lhels_dada2.m1)

# Description*Week effect
oh_Lhels_dada2 <- allEffects(oh_Lhels_dada2.m1)
print(oh_Lhels_dada2)

# Create a data frame
df_oh_Lhels_dada2 <- data.frame(oh_Lhels_dada2$`Description:Week`)

# Statistical analysis
emmeans(oh_Lhels_dada2.m1, pairwise~Description|Week)

# Plot
OH_Lhels_dada2 <- ggplot(data = df_oh_Lhels_dada2,
       aes(x = Week, y = fit, group = Description, color = Description)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), size = 1, width = 0, position = position_dodge(width = 0.4)) + 
  geom_line(size = 1, position = position_dodge(width = 0.4), alpha = 0.2, linetype = "dashed") +
  geom_point(size = 4, aes(shape = Description), position = position_dodge(width = 0.4)) +
  scale_shape_manual(values = c(16,17)) +
  scale_y_continuous(trans = "log10") + 
  scale_color_manual(values=c('#999999', '#E69F00')) +
  annotation_logticks(base = 10, side = "l") +
  theme_classic() +
  ggtitle("Lactobacillus helsingborgensis") +
  theme(plot.title = element_text(face = "italic", size = 10, hjust = 0.5)) +
  theme(axis.text.x = element_text(color = "black", size = 10),
        axis.text.y = element_text(color = "black", size = 10)) +
  theme(axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 10)) +
  ylab(bquote(~Log[10]~ '16S rDNA copies')) +
  theme(legend.position = "none")
```

# For Lactobacillus Firm-5 - Lactobacillus kullabergensis
```{r}
# Model
oh_Lkul_dada2.m1 <- glmer(L_kullabergensis ~ Description*Week + (1 | Hive/Bee), family = poisson, data = out_hive_dada2)
summary(oh_Lkul_dada2.m1)

# anova
Anova(oh_Lkul_dada2.m1)

# Statistical analysis
emmeans(oh_Lkul_dada2.m1, pairwise~Description|Week)
```

# For Lactobacillus Firm-5 - Lactobacillus melliventris
```{r}
# Model
oh_Lmel_dada2.m2 <- glmer(L_melliventris ~ Description*Week + (1 | Hive/Bee), family = poisson, data = out_hive_dada2)
# Model failed and tried to increase the number of iterations, based on this reference: https://rstudio-pubs-static.s3.amazonaws.com/33653_57fc7b8e5d484c909b615d8633c01d51.html)
mell <- getME(oh_Lmel_dada2.m2, c("theta", "fixef"))
oh_Lmel_dada2.m1 <- update(oh_Lmel_dada2.m2, start = mell, control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5)))
summary(oh_Lmel_dada2.m1)

#anova
Anova(oh_Lmel_dada2.m1)

# Statistical analysis
emmeans(oh_Lmel_dada2.m1, pairwise~Description|Week)
```

# For Gilliamella:
```{r}
# Model
oh_gill_dada2.m1 <- glmer(Gilliamella ~ Description*Week + (1 | Hive/Bee), family = poisson, data = out_hive_dada2)
summary(oh_gill_dada2.m1)

# anova
Anova(oh_gill_dada2.m1)

# Description*Week effect
oh_gill_dada2 <- allEffects(oh_gill_dada2.m1)
print(oh_gill_dada2)

# Statistical analysis
emmeans(oh_gill_dada2.m1, pairwise~Description|Week)

# Create a data frame
df_oh_gill_dada2 <- data.frame(oh_gill_dada2$`Description:Week`)

# Plot
OH_GA_dada2 <- ggplot(data = df_oh_gill_dada2,
       aes(x = Week, y = fit, group = Description, color = Description)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), size = 1, width = 0, position = position_dodge(width = 0.4)) + 
  geom_line(size = 1, position = position_dodge(width = 0.4), alpha = 0.2, linetype = "dashed") +
  geom_point(size = 4, aes(shape = Description), position = position_dodge(width = 0.4)) +
  scale_shape_manual(values = c(16,17)) +
  scale_y_continuous(trans = "log10") + 
  scale_color_manual(values=c('#999999', '#E69F00')) +
  annotation_logticks(base = 10, side = "l") +
  theme_classic() +
  ggtitle("Gilliamella spp.") +
  theme(plot.title = element_text(face = "italic", size = 10, hjust = 0.5)) +
  theme(axis.text.x = element_text(color = "black", size = 10),
        axis.text.y = element_text(color = "black", size = 10)) +
  theme(axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 10)) +
  ylab(bquote(~Log[10]~ '16S rDNA copies')) +
  theme(legend.position = "none")
```

# For Bartonella:
```{r}
# Model
oh_bart_dada2.m1 <- glmer(Bartonella ~ Description*Week + (1 | Bee), family = poisson, data = out_hive_dada2)
# Model failed to converge > decided to remove "Hive" as a random effect and increase # of iterations, based on this reference:
# https://rstudio-pubs-static.s3.amazonaws.com/33653_57fc7b8e5d484c909b615d8633c01d51.html)
ev <- getME(oh_bart_dada2.m1, c("theta", "fixef"))
oh_bart_dada2.m2 <- update(oh_bart_dada2.m1, start = ev, control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5)))
summary(oh_bart_dada2.m2)

# anova
Anova(oh_bart_dada2.m2)

# Description*Week effect
oh_bart_dada2 <- allEffects(oh_bart_dada2.m2)
print(oh_bart_dada2)

# Statistical analysis
emmeans(oh_bart_dada2.m2, pairwise~Description|Week)

# Create a data frame
df_oh_bart_dada2 <- data.frame(oh_bart_dada2$`Description:Week`)

# Plot
OH_BA_dada2 <- ggplot(data = df_oh_bart_dada2,
       aes(x = Week, y = fit, group = Description, color = Description)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), size = 1, width = 0, position = position_dodge(width = 0.4)) + 
  geom_line(size = 1, position = position_dodge(width = 0.4), alpha = 0.2, linetype = "dashed") +
  geom_point(size = 4, aes(shape = Description), position = position_dodge(width = 0.4)) +
  scale_shape_manual(values = c(16,17)) +
  scale_y_continuous(trans = "log10") + 
  scale_color_manual(values=c('#999999', '#E69F00')) +
  annotation_logticks(base = 10, side = "l") +
  theme_classic() +
  ggtitle("Bartonella apis") +
  theme(plot.title = element_text(face = "italic", size = 10, hjust = 0.5)) +
  theme(axis.text.x = element_text(color = "black", size = 10), 
        axis.text.y = element_text(color = "black", size = 10)) +
  theme(axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 10)) +
  ylab(bquote(~Log[10]~ '16S rDNA copies')) +
  theme(legend.position = "none")
```

# For Frischella:
```{r}
# Model
oh_fris_dada2.m1 <- glmer(Frischella ~ Description*Week + (1 | Bee), family = poisson, data = out_hive_dada2)
# Model failed and tried to increase the number of iterations, based on this reference: 
# https://rstudio-pubs-static.s3.amazonaws.com/33653_57fc7b8e5d484c909b615d8633c01d51.html)
em <- getME(oh_fris_dada2.m1, c("theta", "fixef"))
oh_fris_dada2.m2 <- update(oh_fris_dada2.m1, start = em, control = glmerControl(optimizer = "bobyqa",
                                                                            optCtrl = list(maxfun = 2e5)))
summary(oh_fris_dada2.m2)

#anova
Anova(oh_fris_dada2.m2)

# Description*Week effect
oh_fris_dada2 <- allEffects(oh_fris_dada2.m2)
print(oh_fris_dada2)

# Statistical analysis
emmeans(oh_fris_dada2.m2, pairwise~Description|Week)

# Create a data frame
df_oh_fris_dada2 <- data.frame(oh_fris_dada2$`Description:Week`)

# Plot
OH_FP_dada2 <- ggplot(data = df_oh_fris_dada2,
       aes(x = Week, y = fit, group = Description, color = Description)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), size = 1, width = 0, position = position_dodge(width = 0.4)) + 
  geom_line(size = 1, position = position_dodge(width = 0.4), alpha = 0.2, linetype = "dashed") +
  geom_point(size = 4, aes(shape = Description), position = position_dodge(width = 0.4)) +
  scale_shape_manual(values = c(16,17)) +
  scale_y_continuous(trans = "log10") + 
  scale_color_manual(values=c('#999999', '#E69F00')) +
  annotation_logticks(base = 10, side = "l") +
  theme_classic() +
  ggtitle("Frischella perrara") +
  theme(plot.title = element_text(face = "italic", size = 10, hjust = 0.5)) +
  theme(axis.text.x = element_text(color = "black", size = 10),
        axis.text.y = element_text(color = "black", size = 10)) +
  theme(axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 10)) +
  ylab(bquote(~Log[10]~ '16S rDNA copies')) +
  theme(legend.position = "none")
```

# For Commensalibacter:
```{r}
# Model
oh_comens_dada2.m1 <- glmer(Commensalibacter ~ Description*Week + (1 | Hive/Bee), family = poisson, data = out_hive_dada2)
# Model failed and tried to increase the number of iterations, based on this reference: https://rstudio-pubs-static.s3.amazonaws.com/33653_57fc7b8e5d484c909b615d8633c01d51.html)
se <- getME(model_alpha21, c("theta", "fixef"))
oh_comens_dada2.m2 <- update(oh_comens_dada2.m1, start = dm, control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5)))
summary(oh_comens_dada2.m2)

# anova
Anova(oh_comens_dada2.m2)

# Description*Week effect
oh_comens_dada2 <- allEffects(oh_comens_dada2.m2)
print(oh_comens_dada2)

# Statistical analysis
emmeans(oh_comens_dada2.m2, pairwise~Description|Week)

# Create a data frame
df_oh_comens_dada2 <- data.frame(oh_comens_dada2$`Description:Week`)

# Plot
OH_CO_dada2 <- ggplot(data = df_oh_comens_dada2,
       aes(x = Week, y = fit, group = Description, color = Description)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), size = 1, width = 0, position = position_dodge(width = 0.4)) + 
  geom_line(size = 1, position = position_dodge(width = 0.4), alpha = 0.2, linetype = "dashed") +
  geom_point(size = 4, aes(shape = Description), position = position_dodge(width = 0.4)) +
  scale_shape_manual(values = c(16,17)) +
  scale_y_continuous(trans = "log10") + 
  scale_color_manual(values=c('#999999', '#E69F00')) +
  annotation_logticks(base = 10, side = "l") +
  theme_classic() +
  ggtitle("Commensalibacter spp.") +
  theme(plot.title = element_text(face = "plain", size = 10, hjust = 0.5)) +
  theme(axis.text.x = element_text(color = "black", size = 10), 
        axis.text.y = element_text(color = "black", size = 10)) +
  theme(axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 10)) +
  ylab(bquote(~Log[10]~ '16S rDNA copies')) +
  theme(legend.position = "none")
```

#For Fructobacillus:
```{r}
# Model
oh_fruct_dada2.m1 <- glmer(Fructobacillus ~ Description*Week + (1 | Hive/Bee), family = poisson, data = out_hive_dada2)
# Model failed and tried to increase the number of iterations, based on this reference: https://rstudio-pubs-static.s3.amazonaws.com/33653_57fc7b8e5d484c909b615d8633c01d51.html)
kl <- getME(oh_fruct_dada2.m1, c("theta", "fixef"))
oh_fruct_dada2.m2 <- update(oh_fruct_dada2.m1, start = kl, control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5)))
summary(oh_fruct_dada2.m2)
# anova
Anova(oh_fruct_dada2.m2)

# Description*Week effect
oh_fruct_dada2 <- allEffects(oh_fruct_dada2.m2)
print(oh_fruct_dada2)

# Statistical analysis
emmeans(oh_fruct_dada2.m2, pairwise~Description|Week)

# Create a data frame
df_oh_fruct_dada2 <- data.frame(oh_fruct_dada2$`Description:Week`)

# Plot
OH_FR_dada2 <- ggplot(data = df_oh_fruct_dada2,
       aes(x = Week, y = fit, group = Description, color = Description)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), size = 1, width = 0, position = position_dodge(width = 0.4)) + 
  geom_line(size = 1, position = position_dodge(width = 0.4), alpha = 0.2, linetype = "dashed") +
  geom_point(size = 4, aes(shape = Description), position = position_dodge(width = 0.4)) +
  scale_shape_manual(values = c(16,17)) +
  scale_y_continuous(trans = "log10") + 
  scale_color_manual(values=c('#999999', '#E69F00')) +
  annotation_logticks(base = 10, side = "l") +
  theme_classic() +
  ggtitle("Fructobacillus spp.") +
  theme(plot.title = element_text(face = "italic", size = 10, hjust = 0.5)) +
  theme(axis.text.x = element_text(color = "black", size = 10), 
        axis.text.y = element_text(color = "black", size = 10)) +
  theme(axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 10)) +
  ylab(bquote(~Log[10]~ '16S rDNA copies')) +
  theme(legend.position = "none")
```

# For L_kunkeei:
```{r}
# Model
oh_other_lact_dada2.m1 <- glmer(L_kunkeei ~ Description*Week + (1 | Hive/Bee), family = poisson, data = out_hive_dada2)
# Model failed and tried to increase the number of iterations, based on this reference: https://rstudio-pubs-static.s3.amazonaws.com/33653_57fc7b8e5d484c909b615d8633c01d51.html)
za <- getME(oh_other_lact_dada2.m1, c("theta", "fixef"))
oh_other_lact_dada2.m2 <- update(oh_other_lact_dada2.m1, start = za, control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5)))
summary(oh_other_lact_dada2.m2)

# anova
Anova(oh_other_lact_dada2.m2)

# Description*Week effect
oh_other_lact_dada2 <- allEffects(oh_other_lact_dada2.m2)
print(oh_other_lact_dada2)

# Statistical analysis
emmeans(oh_other_lact_dada2.m2, pairwise~Description|Week)

# Create a data frame
df_kunkeei <- data.frame(oh_other_lact_dada2$`Description:Week`)

# Plot
OH_LK <- ggplot(data = df_kunkeei,
       aes(x = Week, y = fit, group = Description, color = Description)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), size = 1, width = 0, position = position_dodge(width = 0.4)) + 
  geom_line(size = 1, position = position_dodge(width = 0.4), alpha = 0.2, linetype = "dashed") +
  geom_point(size = 4, aes(shape = Description), position = position_dodge(width = 0.4)) +
  scale_shape_manual(values = c(16,17)) +
  scale_y_continuous(trans = "log10") + 
  scale_color_manual(values=c('#999999', '#E69F00')) +
  annotation_logticks(base = 10, side = "l") +
  theme_classic() +
  ggtitle("Lactobacillus kunkeei") +
  theme(plot.title = element_text(face = "italic", size = 10, hjust = 0.5)) +
  theme(axis.text.x = element_text(color = "black", size = 10),
        axis.text.y = element_text(color = "black", size = 10)) +
  theme(axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 10)) +
  ylab(bquote(~Log[10]~ '16S rDNA copies')) +
  theme(legend.position = "none")
```

### Plotting Figure 3-B,C,D and Figure S4
```{r plot}
### Figure 3-B-C-D:
plot_grid(OH_TB_dada2, OH_SA_dada2, OH_BI_dada2, ncol = 3, labels = "AUTO")

### Figure S4:
plot_grid(OH_F4_dada2, OH_mellis_dada2, OH_mellifer_dada2, OH_F5_dada2, OH_Lapis_dada2, OH_Lhels_dada2, OH_GA_dada2, OH_BA_dada2, OH_FP_dada2, OH_CO_dada2, OH_FR_dada2, OH_LK, ncol = 3, labels = "AUTO")
```
