---
title: "R Scripts for Figures 6C, 7C, 7B, S8, S10 and S11"
author: "Erick Motta"
---

### Experiments related to topical exposure of honey bees to glyphosate-based formulation

### Load packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(interactions)
library(car)
library(tidyverse)
library(ggplot2)
library(FSA) ### for Dunn's test
library(cowplot)
library(patchwork) ### for plotting graphs together
library(gridExtra)
```

### LABORATORY EXPERIMENTS
# Snodgrassella abundance in surviving bees
```{r}
top_exp_lab <- read.table("tables/topical-exp-hive-2019.txt", header = T)

### Boxplot:
df_top_exp_lab <- data.frame(top_exp_lab)
df_top_exp_lab$Description <- factor(df_top_exp_lab$Description, levels = c("Control", "0.05R", "0.1R", "0.5R", "1R", "3R"))

BOXPLOT_top_exp_lab <- ggplot(data = df_top_exp_lab, aes(x = Description, y = Snod_qpcr, fill = Description, color = Description)) +
  geom_boxplot(outlier.size = 0.5, position = position_dodge(width = 0.5)) +
  scale_fill_manual(values=c('#66CCFE', '#F3DA7E', '#F4BD6C', '#E2925E', '#C05E4F', '#8E053A')) +
  scale_color_manual(values=c('#000000', '#000000', '#000000', '#000000', '#000000', '#000000')) +
  scale_y_continuous(trans = "log10", limits = c(1, 100000000)) + 
  annotation_logticks(base = 10, side = "l") +
  ggtitle("Snodgrassella abundance in surviving bees") +
  theme_classic() +
  theme(plot.title = element_text(face = "plain", size = 10, hjust = 0.5)) +
  theme(axis.text.x = element_text(color = "black", size = 10), 
        axis.text.y = element_text(color = "black", size = 10)) +
  theme(axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 10)) +
  ylab(bquote(~Log[10]~ '16S rDNA copies')) +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +
  theme(legend.position="right") +
  theme(legend.direction = "vertical") +
  scale_x_discrete(expand=c(0.2,0))

# Statistical analysis:
kruskal.test(Snod_qpcr ~ Description, data = df_top_exp_lab)
dunnTest(Snod_qpcr ~ Description, data = df_top_exp_lab, method = "bh")
```

# Survival after spray under laboratory conditions 
# Two groups (water and 1.0R)
# Two replicates
```{r Model}
### First replicate 
# Survival after 6 h
top2 <- data.frame(supp=rep(c("Survived", "Died"), each=2),
                 group=rep(c("Water", "1.0R"), 2),
                 len=c(434, 375, 2, 61))
head(top2)

top2$group <- factor(top2$group, levels = c("Water", "1.0R"))

graph_top2 <- ggplot(data = top2, aes(x = group, y = len, fill = supp)) +
  geom_bar(stat = "identity") +
  scale_fill_manual("len", values = c("Died" = "#CCCCCB", "Survived" = "black")) +
  scale_y_continuous("Survival after 6 h", breaks = c(0, 50, 100, 150, 200, 250, 300, 350, 400, 450)) +
  ggtitle("Topical exposure 2") +
  theme(plot.title = element_text(size = 12, face = "plain")) +
  theme(legend.position = "bottom") +
  theme(legend.title = element_blank()) +
  theme(axis.title.x = element_blank()) +
  theme(axis.text.x = element_text(color = "black", size = 10), 
        axis.text.y = element_text(color = "black", size = 10)) +
  theme(axis.title.y = element_text(size = 10))

### Second replicate
# Survival after 6 h
top3 <- data.frame(supp=rep(c("Survived", "Died"), each=2),
                 group=rep(c("Water", "1.0R"), 2),
                 len=c(384, 336, 1, 50))
head(top3)

top3$group <- factor(top3$group, levels = c("Water", "1.0R"))

graph_top3 <- ggplot(data = top3, aes(x = group, y = len, fill = supp)) +
  geom_bar(stat = "identity") +
  scale_fill_manual("len", values = c("Died" = "#CCCCCB", "Survived" = "black")) +
  scale_y_continuous("Survival after 6 h", breaks = c(0, 50, 100, 150, 200, 250, 300, 350, 400, 450)) +
  ggtitle("Topical exposure 3") +
  theme(plot.title = element_text(size = 12, face = "plain")) +
  theme(legend.position = "bottom") +
  theme(legend.title = element_blank()) +
  theme(axis.title.x = element_blank()) +
  theme(axis.text.x = element_text(color = "black", size = 10), 
        axis.text.y = element_text(color = "black", size = 10)) +
  theme(axis.title.y = element_text(size = 10))
```

# Survival after spray under laboratory conditions 
# Four groups (water, 0.1R, 1.0R and 1.0G)
# First replicate
```{r Model}
### First replicate
# Survival after 6 h
top4_1 <- data.frame(supp=rep(c("Survived", "Died"), each=4),
                 group=rep(c("Water", "0.1R", "1.0R", "1.0G"), 2),
                 len=c(372, 360, 335, 378, 16, 28, 51, 10))
head(top4_1)

top4_1$group <- factor(top4_1$group, levels = c("Water", "0.1R", "1.0R", "1.0G"))

graph_top4_1 <- ggplot(data = top4_1, aes(x = group, y = len, fill = supp)) +
  geom_bar(stat = "identity") +
  scale_fill_manual("len", values = c("Died" = "#CCCCCB", "Survived" = "black")) +
  scale_y_continuous("Survival after 6 h", breaks = c(0, 50, 100, 150, 200, 250, 300, 350, 400, 450)) +
  ggtitle("Topical exposure 4") +
  theme(plot.title = element_text(size = 12, face = "plain")) +
  theme(legend.position = "bottom") +
  theme(legend.title = element_blank()) +
  theme(axis.title.x = element_blank()) +
  theme(axis.text.x = element_text(color = "black", size = 10), 
        axis.text.y = element_text(color = "black", size = 10)) +
  theme(axis.title.y = element_text(size = 10))

# Survival after 1 d
top4_2 <- data.frame(supp=rep(c("Survived", "Died"), each=4),
                 group=rep(c("Water", "0.1R", "1.0R", "1.0G"), 2),
                 len=c(355, 346, 76, 363, 33, 42, 310, 25))
head(top4_2)

top4_2$group <- factor(top4_2$group, levels = c("Water", "0.1R", "1.0R", "1.0G"))

graph_top4_2 <- ggplot(data = top4_2, aes(x = group, y = len, fill = supp)) +
  geom_bar(stat = "identity") +
  scale_fill_manual("len", values = c("Died" = "#CCCCCB", "Survived" = "black")) +
  scale_y_continuous("Survival after 1 d", breaks = c(0, 50, 100, 150, 200, 250, 300, 350, 400, 450)) +
  ggtitle("Topical exposure 4") +
  theme(plot.title = element_text(size = 12, face = "plain")) +
  theme(legend.position = "bottom") +
  theme(legend.title = element_blank()) +
  theme(axis.title.x = element_blank()) +
  theme(axis.text.x = element_text(color = "black", size = 10), 
        axis.text.y = element_text(color = "black", size = 10)) +
  theme(axis.title.y = element_text(size = 10))
```

# Survival after spray under laboratory conditions 
# Four groups (water, 0.1R, 1.0R and 1.0G)
# Second replicate
```{r Model}
# Survival after 6 h
top5_1 <- data.frame(supp=rep(c("Survived", "Died"), each=4),
                 group=rep(c("Water", "0.1R", "1.0R", "1.0G"), 2),
                 len=c(264, 261, 257, 265, 2, 5, 9, 1))
head(top5_1)

top5_1$group <- factor(top5_1$group, levels = c("Water", "0.1R", "1.0R", "1.0G"))

graph_top5_1 <- ggplot(data = top5_1, aes(x = group, y = len, fill = supp)) +
  geom_bar(stat = "identity") +
  scale_fill_manual("len", values = c("Died" = "#CCCCCB", "Survived" = "black")) +
  scale_y_continuous("Survival after 6 h", breaks = c(0, 50, 100, 150, 200, 250, 300, 350, 400, 450)) +
  ggtitle("Topical exposure 5") +
  theme(plot.title = element_text(size = 12, face = "plain")) +
  theme(legend.position = "bottom") +
  theme(legend.title = element_blank()) +
  theme(axis.title.x = element_blank()) +
  theme(axis.text.x = element_text(color = "black", size = 10),
        axis.text.y = element_text(color = "black", size = 10)) +
  theme(axis.title.y = element_text(size = 10))

# Survival after 9 h
top5_2 <- data.frame(supp=rep(c("Survived", "Died"), each=4),
                 group=rep(c("Water", "0.1R", "1.0R", "1.0G"), 2),
                 len=c(262, 256, 182, 264, 4, 10, 84, 2))
head(top5_2)

top5_2$group <- factor(top5_2$group, levels = c("Water", "0.1R", "1.0R", "1.0G"))

graph_top5_2 <- ggplot(data = top5_2, aes(x = group, y = len, fill = supp)) +
  geom_bar(stat = "identity") +
  scale_fill_manual("len", values = c("Died" = "#CCCCCB", "Survived" = "black")) +
  scale_y_continuous("Survival after 9 h", breaks = c(0, 50, 100, 150, 200, 250, 300, 350, 400, 450)) +
  ggtitle("Topical exposure 5") +
  theme(plot.title = element_text(size = 12, face = "plain")) +
  theme(legend.position = "bottom") +
  theme(legend.title = element_blank()) +
  theme(axis.title.x = element_blank()) +
  theme(axis.text.x = element_text(color = "black", size = 10),
        axis.text.y = element_text(color = "black", size = 10)) +
  theme(axis.title.y = element_text(size = 10))

# Survival after 12 h
top5_3 <- data.frame(supp=rep(c("Survived", "Died"), each=4),
                 group=rep(c("Water", "0.1R", "1.0R", "1.0G"), 2),
                 len=c(262, 253, 50, 264, 4, 13, 216, 2))
head(top5_3)

top5_3$group <- factor(top5_3$group, levels = c("Water", "0.1R", "1.0R", "1.0G"))

graph_top5_3 <- ggplot(data = top5_3, aes(x = group, y = len, fill = supp)) +
  geom_bar(stat = "identity") +
  scale_fill_manual("len", values = c("Died" = "#CCCCCB", "Survived" = "black")) +
  scale_y_continuous("Survival after 12 h", breaks = c(0, 50, 100, 150, 200, 250, 300, 350, 400, 450)) +
  ggtitle("Topical exposure 5") +
  theme(plot.title = element_text(size = 12, face = "plain")) +
  theme(legend.position = "bottom") +
  theme(legend.title = element_blank()) +
  theme(axis.title.x = element_blank()) +
  theme(axis.text.x = element_text(color = "black", size = 10),
        axis.text.y = element_text(color = "black", size = 10)) +
  theme(axis.title.y = element_text(size = 10))

# Survival after 24 h
top5_4 <- data.frame(supp=rep(c("Survived", "Died"), each=4),
                 group=rep(c("Water", "0.1R", "1.0R", "1.0G"), 2),
                 len=c(261, 205, 1, 263, 5, 61, 265, 3))
head(top5_4)

top5_4$group <- factor(top5_3$group, levels = c("Water", "0.1R", "1.0R", "1.0G"))

graph_top5_4 <- ggplot(data = top5_4, aes(x = group, y = len, fill = supp)) +
  geom_bar(stat = "identity") +
  scale_fill_manual("len", values = c("Died" = "#CCCCCB", "Survived" = "black")) +
  scale_y_continuous("Survival after 24 h", breaks = c(0, 50, 100, 150, 200, 250, 300, 350, 400, 450)) +
  ggtitle("Topical exposure 5") +
  theme(plot.title = element_text(size = 12, face = "plain")) +
  theme(legend.position = "bottom") +
  theme(legend.title = element_blank()) +
  theme(axis.title.x = element_blank()) +
  theme(axis.text.x = element_text(color = "black", size = 10), 
        axis.text.y = element_text(color = "black", size = 10)) +
  theme(axis.title.y = element_text(size = 10))
```

# Survival after spray under laboratory conditions 
# Six groups (water, 0.05R, 0.1R, 0.5R, 1.0R and 3.0R)
# First replicate
```{r Model}
# Survival after 6 h
top10_1 <- data.frame(supp=rep(c("Survived", "Died"), each=6),
                 group=rep(c("Water", "0.05R", "0.1R", "0.5R", "1.0R", "3.0R"), 2),
                 len=c(395,394,392,388,388,364,2,3,4,8,9,33))
head(top10_1)

top10_1$group <- factor(top10_1$group, levels = c("Water", "0.05R", "0.1R", "0.5R", "1.0R", "3.0R"))

graph_top10_1 <- ggplot(data = top10_1, aes(x = group, y = len, fill = supp)) +
  geom_bar(stat = "identity") +
  scale_fill_manual("len", values = c("Died" = "#CCCCCB", "Survived" = "black")) +
  scale_y_continuous("Survival after 6 h", breaks = c(0, 50, 100, 150, 200, 250, 300, 350, 400, 450)) +
  ggtitle("Topical exposure 10") +
  theme(plot.title = element_text(size = 12, face = "plain")) +
  theme(legend.position = "bottom") +
  theme(legend.title = element_blank()) +
  theme(axis.title.x = element_blank()) +
  theme(axis.text.x = element_text(color = "black", size = 10), 
        axis.text.y = element_text(color = "black", size = 10)) +
  theme(axis.title.y = element_text(size = 10))

# Survival after 9 h
top10_2 <- data.frame(supp=rep(c("Survived", "Died"), each=6),
                 group=rep(c("Water", "0.05R", "0.1R", "0.5R", "1.0R", "3.0R"), 2),
                 len=c(393,393,391,380,375,340,4,4,5,16,22,57))
head(top10_2)

top10_2$group <- factor(top10_2$group, levels = c("Water", "0.05R", "0.1R", "0.5R", "1.0R", "3.0R"))

graph_top10_2 <- ggplot(data = top10_2, aes(x = group, y = len, fill = supp)) +
  geom_bar(stat = "identity") +
  scale_fill_manual("len", values = c("Died" = "#CCCCCB", "Survived" = "black")) +
  scale_y_continuous("Survival after 9 h", breaks = c(0, 50, 100, 150, 200, 250, 300, 350, 400, 450)) +
  ggtitle("Topical exposure 10") +
  theme(plot.title = element_text(size = 12, face = "plain")) +
  theme(legend.position = "bottom") +
  theme(legend.title = element_blank()) +
  theme(axis.title.x = element_blank()) +
  theme(axis.text.x = element_text(color = "black", size = 10), 
        axis.text.y = element_text(color = "black", size = 10)) +
  theme(axis.title.y = element_text(size = 10))

# Survival after 12 h
top10_3 <- data.frame(supp=rep(c("Survived", "Died"), each=6),
                 group=rep(c("Water", "0.05R", "0.1R", "0.5R", "1.0R", "3.0R"), 2),
                 len=c(393,390,390,375,350,307,4,7,6,21,47,90))
head(top10_3)

top10_3$group <- factor(top10_3$group, levels = c("Water", "0.05R", "0.1R", "0.5R", "1.0R", "3.0R"))

graph_top10_3 <- ggplot(data = top10_3, aes(x = group, y = len, fill = supp)) +
  geom_bar(stat = "identity") +
  scale_fill_manual("len", values = c("Died" = "#CCCCCB", "Survived" = "black")) +
  scale_y_continuous("Survival after 12 h", breaks = c(0, 50, 100, 150, 200, 250, 300, 350, 400, 450)) +
  ggtitle("Topical exposure 10") +
  theme(plot.title = element_text(size = 12, face = "plain")) +
  theme(legend.position = "bottom") +
  theme(legend.title = element_blank()) +
  theme(axis.title.x = element_blank()) +
  theme(axis.text.x = element_text(color = "black", size = 10), 
        axis.text.y = element_text(color = "black", size = 10)) +
  theme(axis.title.y = element_text(size = 10))

# Survival after 24 h
top10_4 <- data.frame(supp=rep(c("Survived", "Died"), each=6),
                 group=rep(c("Water", "0.05R", "0.1R", "0.5R", "1.0R", "3.0R"), 2),
                 len=c(381,373,364,312,222,68,16,24,32,84,175,329))
head(top10_4)

top10_4$group <- factor(top10_4$group, levels = c("Water", "0.05R", "0.1R", "0.5R", "1.0R", "3.0R"))

graph_top10_4 <- ggplot(data = top10_4, aes(x = group, y = len, fill = supp)) +
  geom_bar(stat = "identity") +
  scale_fill_manual("len", values = c("Died" = "#CCCCCB", "Survived" = "black")) +
  scale_y_continuous("Survival after 24 h", breaks = c(0, 50, 100, 150, 200, 250, 300, 350, 400, 450)) +
  ggtitle("Topical exposure 10") +
  theme(plot.title = element_text(size = 12, face = "plain")) +
  theme_classic() +
  theme(legend.position = "bottom") +
  theme(legend.title = element_blank()) +
  theme(axis.title.x = element_blank()) +
  theme(axis.text.x = element_text(color = "black", size = 10), 
        axis.text.y = element_text(color = "black", size = 10)) +
  theme(axis.title.y = element_text(size = 10))
```

# Survival after spray under laboratory conditions 
# Six groups (water, 0.05R, 0.1R, 0.5R, 1.0R and 3.0R)
# Second replicate
```{r Model}
# Survival after 6 h
top7_1 <- data.frame(supp=rep(c("Survived", "Died"), each=6),
                 group=rep(c("Water", "0.05R", "0.1R", "0.5R", "1.0R", "3.0R"), 2),
                 len=c(310,309,309,310,305,297,0,1,1,0,5,13))
head(top7_1)

top7_1$group <- factor(top7_1$group, levels = c("Water", "0.05R", "0.1R", "0.5R", "1.0R", "3.0R"))

graph_top7_1 <- ggplot(data = top7_1, aes(x = group, y = len, fill = supp)) +
  geom_bar(stat = "identity") +
  scale_fill_manual("len", values = c("Died" = "#CCCCCB", "Survived" = "black")) +
  scale_y_continuous("Survival after 6 h", breaks = c(0, 50, 100, 150, 200, 250, 300, 350, 400, 450)) +
  ggtitle("Topical exposure 7") +
  theme(plot.title = element_text(size = 12, face = "plain")) +
  theme(legend.position = "bottom") +
  theme(legend.title = element_blank()) +
  theme(axis.title.x = element_blank()) +
  theme(axis.text.x = element_text(color = "black", size = 10), 
        axis.text.y = element_text(color = "black", size = 10)) +
  theme(axis.title.y = element_text(size = 10))

# Survival after 9 h
top7_2 <- data.frame(supp=rep(c("Survived", "Died"), each=6),
                 group=rep(c("Water", "0.05R", "0.1R", "0.5R", "1.0R", "3.0R"), 2),
                 len=c(309,307,305,304,300,262,1,3,5,6,10,48))
head(top7_2)

top7_2$group <- factor(top7_2$group, levels = c("Water", "0.05R", "0.1R", "0.5R", "1.0R", "3.0R"))

graph_top7_2 <- ggplot(data = top7_2, aes(x = group, y = len, fill = supp)) +
  geom_bar(stat = "identity") +
  scale_fill_manual("len", values = c("Died" = "#CCCCCB", "Survived" = "black")) +
  scale_y_continuous("Survival after 9 h", breaks = c(0, 50, 100, 150, 200, 250, 300, 350, 400, 450)) +
  ggtitle("Topical exposure 7") +
  theme(plot.title = element_text(size = 12, face = "plain")) +
  theme(legend.position = "bottom") +
  theme(legend.title = element_blank()) +
  theme(axis.title.x = element_blank()) +
  theme(axis.text.x = element_text(color = "black", size = 10), 
        axis.text.y = element_text(color = "black", size = 10)) +
  theme(axis.title.y = element_text(size = 10))

# Survival after 12 h
top7_3 <- data.frame(supp=rep(c("Survived", "Died"), each=6),
                 group=rep(c("Water", "0.05R", "0.1R", "0.5R", "1.0R", "3.0R"), 2),
                 len=c(308,306,303,299,286,225,2,4,7,11,24,85))
head(top7_3)

top7_3$group <- factor(top7_3$group, levels = c("Water", "0.05R", "0.1R", "0.5R", "1.0R", "3.0R"))

graph_top7_3 <- ggplot(data = top7_3, aes(x = group, y = len, fill = supp)) +
  geom_bar(stat = "identity") +
  scale_fill_manual("len", values = c("Died" = "#CCCCCB", "Survived" = "black")) +
  scale_y_continuous("Survival after 12 h", breaks = c(0, 50, 100, 150, 200, 250, 300, 350, 400, 450)) +
  ggtitle("Topical exposure 7") +
  theme(plot.title = element_text(size = 12, face = "plain")) +
  theme(legend.position = "bottom") +
  theme(legend.title = element_blank()) +
  theme(axis.title.x = element_blank()) +
  theme(axis.text.x = element_text(color = "black", size = 10), 
        axis.text.y = element_text(color = "black", size = 10)) +
  theme(axis.title.y = element_text(size = 10))

# Survival after 24 h
top7_4 <- data.frame(supp=rep(c("Survived", "Died"), each=6),
                 group=rep(c("Water", "0.05R", "0.1R", "0.5R", "1.0R", "3.0R"), 2),
                 len=c(301,292,282,263,110,54,9,18,28,47,200,256))
head(top7_4)

top7_4$group <- factor(top7_4$group, levels = c("Water", "0.05R", "0.1R", "0.5R", "1.0R", "3.0R"))

graph_top7_4 <- ggplot(data = top7_4, aes(x = group, y = len, fill = supp)) +
  geom_bar(stat = "identity") +
  scale_fill_manual("len", values = c("Died" = "#CCCCCB", "Survived" = "black")) +
  scale_y_continuous("Survival after 24 h", breaks = c(0, 50, 100, 150, 200, 250, 300, 350, 400, 450)) +
  ggtitle("Topical exposure 7") +
  theme(plot.title = element_text(size = 12, face = "plain")) +
  theme(legend.position = "bottom") +
  theme(legend.title = element_blank()) +
  theme(axis.title.x = element_blank()) +
  theme(axis.text.x = element_text(color = "black", size = 10), 
        axis.text.y = element_text(color = "black", size = 10)) +
  theme(axis.title.y = element_text(size = 10))
```


### Dose-response for two topical exposure experiments under laboratory conditions:
```{r }
# Load packages
library(tidyverse)
library(zoo)
library(drc)
library(lattice)

### First replicate

# Load data:
spray_survival_10th
names(spray_survival_10th)

# Run regression model:
spray_survival_10th.m1 <- drm(bees~round_conc, hour, data = spray_survival_10th,
                            fct = LL.4(names = c("Slope", "Lower limit", "Upper limit", "EC50")))
summary(spray_survival_10th.m1)

dose_resp_10th <- plot(spray_survival_10th.m1, pch = c(16,17), cex = 1, col = c("#00AFBB", "#E7B800"), bg = "white", broken= TRUE, type = "all",
     xlab = "Roundup (%)",
     ylab = "Survived bees per cup cage")

modelFit(spray_survival_10th.m1)

ED(spray_survival_10th.m1, c(5, 10, 50), interval = "delta")

### Second replicate

# Load data:
spray_survival_6th
names(spray_survival_6th)

# Run regression model:
spray_survival_6th.m1 <- drm(bees~round_conc, hour, data = spray_survival_6th,
                              fct = LL.4(names = c("Slope", "Lower limit", "Upper limit", "EC50")))
summary(spray_survival_6th.m1)

dose_resp_6th <- plot(spray_survival_6th.m1, pch = c(16,17), cex = 1, col = c("#00AFBB", "#E7B800"), bg = "white", broken= TRUE, type = "all",
     xlab = "Roundup (%)",
     ylab = "Survived bees per cup cage")

modelFit(spray_survival_6th.m1)

ED(spray_survival_10th.m1, c(5, 10, 50), interval = "delta")
```

#####
#####
#####

### HIVE EXPERIMENTS
# Snodgrassella abundance in recovered bees
```{r}
top_exp_hive <- read.table("tables/topical-exp-hive-2019.txt", header = T)

### Boxplot:
df_top_exp_hive <- data.frame(top_exp_hive)
df_top_exp_hive$Description <- factor(df_top_exp_hive$Description, levels = c("Control", "0.05R", "0.1R", "0.5R", "1R", "3R"))

BOXPLOT_top_exp_hive <- ggplot(data = df_top_exp_hive, aes(x = Description, y = Snod_qpcr, fill = Description, color = Description)) +
  geom_boxplot(outlier.size = 0.5, position = position_dodge(width = 0.5)) +
  scale_fill_manual(values=c('#66CCFE', '#F3DA7E', '#F4BD6C', '#E2925E', '#C05E4F', '#8E053A')) +
  scale_color_manual(values=c('#000000', '#000000', '#000000', '#000000', '#000000', '#000000')) +
  scale_y_continuous(trans = "log10", limits = c(100, 100000000)) + 
  annotation_logticks(base = 10, side = "l") +
  ggtitle("Snodgrassella abundance in recovered bees") +
  theme_classic() +
  theme(plot.title = element_text(face = "plain", size = 10, hjust = 0.5)) +
  theme(axis.text.x = element_text(color = "black", size = 10), 
        axis.text.y = element_text(color = "black", size = 10)) +
  theme(axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 10)) +
  ylab(bquote(~Log[10]~ '16S rDNA copies')) +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +
  theme(legend.position="right") +
  theme(legend.direction = "vertical") +
  scale_x_discrete(expand=c(0.2,0))

# Statistical analysis:
kruskal.test(Snod_qpcr ~ Description, data = df_top_exp_hive)
dunnTest(Snod_qpcr ~ Description, data = df_top_exp_hive, method = "bh")
```

# Hive recovery rates:
# Two groups per time (water and 3.0R, water and 1.0R, water and 1.0R, water and 0.1R)
# Four replicates
```{r Model}
### Water and 3.0R, recovery after 3 d
top6 <- data.frame(supp=rep(c("Recovered", "Non-recovered"), each=2),
                 group=rep(c("Water", "3.0R"), 2),
                 len=c(266,136,129,259))
head(top6)

top6$group <- factor(top6$group, levels = c("Water", "3.0R"))

graph_top6 <- ggplot(data = top6, aes(x = group, y = len, fill = supp)) +
  geom_bar(stat = "identity") +
  scale_fill_manual("len", values = c("Non-recovered" = "#CCCCCB", "Recovered" = "black")) +
  scale_y_continuous("Recovery after 3 d", breaks = c(0, 50, 100, 150, 200, 250, 300, 350, 400)) +
  ggtitle("Topical exposure 6") +
  theme(plot.title = element_text(size = 12, face = "plain")) +
  theme(legend.position = "bottom") +
  theme(legend.title = element_blank()) +
  theme(axis.title.x = element_blank()) +
  theme(axis.text.x = element_text(color = "black", size = 10), 
        axis.text.y = element_text(color = "black", size = 10)) +
  theme(axis.title.y = element_text(size = 10))

### Water and 1.0R, first replicate, recovery after 3 d
top8 <- data.frame(supp=rep(c("Recovered", "Non-recovered"), each=2),
                 group=rep(c("Water", "1.0R"), 2),
                 len=c(92,48,298,342))
head(top8)

top8$group <- factor(top8$group, levels = c("Water", "1.0R"))

graph_top8 <- ggplot(data = top8, aes(x = group, y = len, fill = supp)) +
  geom_bar(stat = "identity") +
  scale_fill_manual("len", values = c("Non-recovered" = "#CCCCCB", "Recovered" = "black")) +
  scale_y_continuous("Recovery after 3 d", breaks = c(0, 50, 100, 150, 200, 250, 300, 350, 400)) +
  ggtitle("Topical exposure 8") +
  theme(plot.title = element_text(size = 12, face = "plain")) +
  theme(legend.position = "bottom") +
  theme(legend.title = element_blank()) +
  theme(axis.title.x = element_blank()) +
  theme(axis.text.x = element_text(color = "black", size = 10), 
        axis.text.y = element_text(color = "black", size = 10)) +
  theme(axis.title.y = element_text(size = 10))

### Water and 1.0R, second replicate, recovery after 3 d
top9 <- data.frame(supp=rep(c("Recovered", "Non-recovered"), each=2),
                 group=rep(c("Water", "1.0R"), 2),
                 len=c(143,63,247,327))
head(top9)

top9$group <- factor(top9$group, levels = c("Water", "1.0R"))

graph_top9 <- ggplot(data = top9, aes(x = group, y = len, fill = supp)) +
  geom_bar(stat = "identity") +
  scale_fill_manual("len", values = c("Non-recovered" = "#CCCCCB", "Recovered" = "black")) +
  scale_y_continuous("Recovery after 3 d", breaks = c(0, 50, 100, 150, 200, 250, 300, 350, 400)) +
  ggtitle("Topical exposure 9") +
  theme(plot.title = element_text(size = 12, face = "plain")) +
  theme(legend.position = "bottom") +
  theme(legend.title = element_blank()) +
  theme(axis.title.x = element_blank()) +
  theme(axis.text.x = element_text(color = "black", size = 10), 
        axis.text.y = element_text(color = "black", size = 10)) +
  theme(axis.title.y = element_text(size = 10))

### Water and 0.1R, recovery after 3 d
top11 <- data.frame(supp=rep(c("Recovered", "Non-recovered"), each=2),
                 group=rep(c("Water", "0.1R"), 2),
                 len=c(88,80,312,320))
head(top11)

top11$group <- factor(top11$group, levels = c("Water", "0.1R"))

graph_top11 <- ggplot(data = top11, aes(x = group, y = len, fill = supp)) +
  geom_bar(stat = "identity") +
  scale_fill_manual("len", values = c("Non-recovered" = "#CCCCCB", "Recovered" = "black")) +
  scale_y_continuous("Recovery after 3 d", breaks = c(0, 50, 100, 150, 200, 250, 300, 350, 400)) +
  ggtitle("Topical exposure 11") +
  theme(plot.title = element_text(size = 12, face = "plain")) +
  theme(legend.position = "bottom") +
  theme(legend.title = element_blank()) +
  theme(axis.title.x = element_blank()) +
  theme(axis.text.x = element_text(color = "black", size = 10), 
        axis.text.y = element_text(color = "black", size = 10)) +
  theme(axis.title.y = element_text(size = 10))
```

# Hive recovery rates:
# Six groups (water, 0.05R, 0.1R, 0.5R, 1.0R and 3.0R)
```{r Model}
### Recovery after 3 d
top12 <- data.frame(supp=rep(c("Recovered", "Non-recovered"), each=6),
                 group=rep(c("Water", "0.05% R", "0.1% R", "0.5% R", "1% R", "3% R"), 2),
                 len=c(124,103,100,70,42,16,136,157,160,190,218,244))
head(top12)

top12$group <- factor(top12$group, levels = c("Water", "0.05% R", "0.1% R", "0.5% R", "1% R", "3% R"))

graph_top12 <- ggplot(data = top12, aes(x = group, y = len, fill = supp)) +
  geom_bar(stat = "identity") +
  scale_fill_manual("len", values = c("Non-recovered" = "#CCCCCB", "Recovered" = "black")) +
  scale_y_continuous("Recovery after 3 d", breaks = c(0,30,60,90,120,150,180,210,240,270)) +
  ggtitle("Topical exposure - Experiment 12") +
  theme(plot.title = element_text(size = 12, face = "plain")) +
  theme(legend.position = "bottom") +
  theme(legend.title = element_blank()) +
  theme(axis.title.x = element_blank()) +
  theme(axis.text.x = element_text(color = "black", size = 10), 
        axis.text.y = element_text(color = "black", size = 10)) +
  theme(axis.title.y = element_text(size = 10))
```

### Plotting Figures:
``` {r}
### Figure 6C:
plot_grid(BOXPLOT_top_exp_lab, labels = "AUTO")

### Figure 7B-C:
plot_grid(graph_top12, BOXPLOT_top_exp_hive, labels = "AUTO")

### Figure S8:
plot_grid(graph_top10_1, graph_top10_2, graph_top10_3, graph_top10_4, graph_top7_1, graph_top7_2, graph_top7_3, graph_top7_4, ncol = 4, labels = "AUTO")

### Figure S9:
dose_resp_10th <- plot(spray_survival_10th.m1, pch = c(16,17), cex = 1, col = c("#00AFBB", "#E7B800"), bg = "white", broken= TRUE, type = "all",
     xlab = "Roundup (%)",
     ylab = "Survived bees per cup cage")

### Figure S10:
plot_grid(graph_top2, graph_top3, graph_top4_1, graph_top4_2, graph_top5_1, graph_top5_2, graph_top5_3, graph_top5_4, ncol = 4, labels = "AUTO")

### Figure S11:
plot_grid(graph_top11, graph_top8, graph_top9, graph_top6, ncol = 4, labels = "AUTO")
```
